Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-08-10 doc/manuscript/ESSDmanuscript.Rmd
remove Valentyna & Sandro from author list

---
title: Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'essd')`"
author:
  - given_name: Madison 
    surname: Williams
    affiliation: "1"
  - given_name: Valentine
    surname: Herrmann
    affiliation: "1"
  - given_name: Rebecca
    surname: Banbury Morgan
    affiliation: "1,2" 
  - given_name: Ben 
    surname: Bond-Lamberty
    affiliation: "3" 
  - given_name: Susan 
    surname: Cook-Patton
    affiliation: "4" 
  - given_name: Sandro 
    surname: Federici 
    affiliation: "5" 
  - given_name: Helene
    surname: Muller-Landau
    affiliation: "6" 
  - given_name: Camille
    surname: Piponiot
    affiliation: "7" 
  - given_name: Teagan
    surname: Rogers
    affiliation: "1"
  - given_name: Valentyna
    surname: Slivinska 
    affiliation: "5"
  - given_name: Kristina J.
    surname: Anderson-Teixeira
    affiliation: "1,6 *"
    email: teixeirak@si.edu
    corresponding: true

@@

affiliation:
  - code: 1
    address: Center for Conservatiton Ecology, Smithsonian Conservation Biology Institute, Front Royal, VA, United States
  - code: 2
    address: School of Geography, University of Leeds, Leeds, UK
  - code: 3
    address: Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD, United States
  - code: 4
    address: The Nature Conservancy; Arlington VA 22203, USA
  - code: 5
    address:  IPCC Task Force on National Greenhouse Gas Inventories Technical Support Unit, Institute for Global Environmental Strategies, Hayama, Japan
  - code: 6
    address: Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Panama, Republic of Panama
  - code: 7
    address: CIRAD, Montpellier, France

>>>>

---
title: Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'essd')`"
author:
  - given_name: Madison 
    surname: Williams
    affiliation: "1"
  - given_name: Valentine
    surname: Herrmann
    affiliation: "1"
  - given_name: Rebecca
    surname: Banbury Morgan
    affiliation: "1,2" 
  - given_name: Ben 
    surname: Bond-Lamberty
    affiliation: "3" 
  - given_name: Susan 
    surname: Cook-Patton
    affiliation: "4" 
  - given_name: Helene
    surname: Muller-Landau
    affiliation: "5" 
  - given_name: Camille
    surname: Piponiot
    affiliation: "6" 
  - given_name: Teagan
    surname: Rogers
    affiliation: "1"
  - given_name: Kristina J.
    surname: Anderson-Teixeira
    affiliation: "1,5 *"
    email: teixeirak@si.edu
    corresponding: true

@@

affiliation:
  - code: 1
    address: Center for Conservatiton Ecology, Smithsonian Conservation Biology Institute, Front Royal, VA, United States
  - code: 2
    address: School of Geography, University of Leeds, Leeds, UK
  - code: 3
    address: Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD, United States
  - code: 4
    address: The Nature Conservancy; Arlington VA 22203, USA
  - code: 5
    address: Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Panama, Republic of Panama
  - code: 6
    address: CIRAD, Montpellier, France

### 2021-08-10 doc/manuscript/ESSDmanuscript.tex
remove Valentyna & Sandro from author list

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

@@

% The "Technical instructions for LaTex" by Copernicus require _not_ to insert any additional packages.
%%\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
%
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\Author[1]{Madison}{Williams}
\Author[1]{Valentine}{Herrmann}
\Author[1,2]{Rebecca}{Banbury Morgan}
\Author[3]{Ben}{Bond-Lamberty}
\Author[4]{Susan}{Cook-Patton}
\Author[5]{Sandro}{Federici}
\Author[6]{Helene}{Muller-Landau}
\Author[7]{Camille}{Piponiot}
\Author[1]{Teagan}{Rogers}
\Author[5]{Valentyna}{Slivinska}
\Author[1,6 *]{Kristina J.}{Anderson-Teixeira}

\affil[1]{Center for Conservatiton Ecology, Smithsonian Conservation
Biology Institute, Front Royal, VA, United States}
\affil[2]{School of Geography, University of Leeds, Leeds, UK}
\affil[3]{Joint Global Change Research Institute, Pacific Northwest
National Laboratory, College Park, MD, United States}
\affil[4]{The Nature Conservancy; Arlington VA 22203, USA}
\affil[5]{IPCC Task Force on National Greenhouse Gas Inventories
Technical Support Unit, Institute for Global Environmental Strategies,
Hayama, Japan}
\affil[6]{Forest Global Earth Observatory, Smithsonian Tropical Research
Institute, Panama, Republic of Panama}
\affil[7]{CIRAD, Montpellier, France}

>>>>

%% Please DO NOT add additional packages or LaTeX commands to the template. They
%% are not supported by Coperncius. LaTeX packages already
%% included in the copernicus.cls are:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

@@

% The "Technical instructions for LaTex" by Copernicus require _not_ to insert any additional packages.
%%\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
%

@@

\Author[1]{Madison}{Williams}
\Author[1]{Valentine}{Herrmann}
\Author[1,2]{Rebecca}{Banbury Morgan}
\Author[3]{Ben}{Bond-Lamberty}
\Author[4]{Susan}{Cook-Patton}
\Author[5]{Helene}{Muller-Landau}
\Author[6]{Camille}{Piponiot}
\Author[1]{Teagan}{Rogers}
\Author[1,5 *]{Kristina J.}{Anderson-Teixeira}

\affil[1]{Center for Conservatiton Ecology, Smithsonian Conservation
Biology Institute, Front Royal, VA, United States}
\affil[2]{School of Geography, University of Leeds, Leeds, UK}
\affil[3]{Joint Global Change Research Institute, Pacific Northwest
National Laboratory, College Park, MD, United States}
\affil[4]{The Nature Conservancy; Arlington VA 22203, USA}
\affil[5]{Forest Global Earth Observatory, Smithsonian Tropical Research
Institute, Panama, Republic of Panama}
\affil[6]{CIRAD, Montpellier, France}
